From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-06 Pi+/paper/equivalence.tex
Remove dangling newlines
working on intro

\section{Going from \texorpdfstring{$\PiLang$}{Pi} to \texorpdfstring{$\UFin$}{UFin} and back}~\label{sec:equivalence}

@@

>>>>

\section{Going from \texorpdfstring{$\PiLang$}{Pi} to \texorpdfstring{$\UFin$}{UFin} and back}
\label{sec:equivalence}

@@

\vc{ The groupoid of finite types is the free symmetric monoidal groupoid on one generator. This can be presented as an
  algebraic 2-theory, which is our syntax for $\PiHatLang$. Vertical categorification of natural numbers as a free
  commutative monoid. See groupoidification. }

### 2021-07-06 Pi+/paper/finite.tex
working on intro

\section{The Group of Permutations}~\label{sec:finite}

@@

\begin{figure}
  \[
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 5,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick]
      {braid={s_1, s_2, s_3, s_4}};
    \end{tikzpicture}
  \]
  \caption{Braiding diagram for $0 \downf 4$}
  \label{fig:downf}
\end{figure}

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 0$ and $k = 3$, it allows for
the reduction $[4, 3, 2, 1, 0, 4] \longcox* [3, 4, 3, 2, 1, 0]$ (see~\cref{fig:longcox}).

\begin{figure}
  \begin{tikzpicture}
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (0, 0)
    {braid={s_5, s_1, s_2, s_3, s_4, s_5}};
    \node[font=\Huge] at (4, 1.3) {\(\rightarrow\)};
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (5, 0)
    {braid={s_1, s_2, s_3, s_4, s_5, s_4}};
  \end{tikzpicture}
  \caption{Braiding diagram for $\longcox$ with $n = 0$ and $k = 3$}
  \label{fig:longcox}
\end{figure}

>>>>

\section{The Group of Permutations}
\label{sec:finite}

@@

\begin{figure}
  \[
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 5,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick]
      {braid={s_4, s_3, s_2, s_1}};
    \end{tikzpicture}
  \]
  \caption{Braiding diagram for $0 \downf 4$}
  \label{fig:downf}
\end{figure}

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 2$ and $k = 3$, it allows for
the reduction $[6, 5, 4, 3, 2, 6] \longcox* [5, 6, 5, 4, 3, 2]$ (see~\cref{fig:longcox} for the braid diagram).

\begin{figure}
  \begin{tikzpicture}
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (0, 0)
    {braid={s_5, s_4, s_3, s_2, s_1, s_5}};
    \node[font=\Huge] at (4, 1.3) {\(\rightarrow\)};
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (5, 0)
    {braid={s_4, s_5, s_4, s_3, s_2, s_1}};
  \end{tikzpicture}
  \caption{Braiding diagram for $\longcox$ with $n = 0$ and $k = 3$}
  \label{fig:longcox}
\end{figure}
